### 2014-01-09 thesis-proposal/problem.tex
Updated figure

%In a conventional \emph{monolithic} programming system, support for each of these features would need to be built into the language and tools. 
No system today has built-in support for all of the features enumerated above. Instead, libraries generally provide support for regular expressions by leveraging  general-purpose constructs. Unfortunately, it is impossible to fully encode the syntax and the specialized static and dynamic semantics described above in terms of general-purpose notations and abstractions. Library providers have thus needed to compromise. The typical choice is to have clients provide regular expressions as strings, deferring parsing, typechecking and elaboration to run-time, which introduces performance overhead and can lead to unanticipated run-time errors (as shown in \cite{spishak2012type}) and security vulnerabilities (due to injection attacks when user inputs are spliced into patterns, for example). Similarly, tools are rarely integrated into editors, and even more rarely in a way that facilitates their discovery and use directly when the developer is manipulating regular expressions. Tools that must be discovered independently and accessed externally (for example, via a browser) are used less frequently  and can be more awkward than necessary \cite{Campbell:2008:DRT:1636642.1636651, Omar:2012:ACC:2337223.2337324}, leading to lower productivity.

\subsection{Language-External Approaches}
\begin{figure}
\begin{center}
\includegraphics[scale=0.45]{approaches.pdf}
\end{center}
\vspace{-20px}
\caption{\small (a) With the language-external approach, novel features are packaged into separate languages and tools. Clients of an API can only safely and naturally use it if the interface uses common constructs (the \emph{compatibility problem}). (b) With the active library approach, there is one extensible host language and the compile-time and edit-time logic governing novel constructs is expressed within libraries. If the extension mechanism guarantees the safety of arbitrary compositions of extensions, the necessary primitives can simply be imported by library clients as needed, and so interoperability is not a problem.}
\label{approaches}
\end{figure}

>>>>

%In a conventional \emph{monolithic} programming system, support for each of these features would need to be built into the language and tools. 
No system today has built-in support for all of the features enumerated above. Instead, libraries generally provide support for regular expressions by leveraging  general-purpose constructs. Unfortunately, it is impossible to fully encode the syntax and the specialized static and dynamic semantics described above in terms of general-purpose notations and abstractions. Library providers have thus needed to compromise. The typical choice is to have clients provide regular expressions as strings, deferring parsing, typechecking and elaboration to run-time, which introduces performance overhead and can lead to unanticipated run-time errors (as shown in \cite{spishak2012type}) and security vulnerabilities (due to injection attacks when user inputs are spliced into patterns, for example). Similarly, tools are rarely integrated into editors, and even more rarely in a way that facilitates their discovery and use directly when the developer is manipulating regular expressions. Tools that must be discovered independently and accessed externally (for example, via a browser) are used less frequently  and can be more awkward than necessary \cite{Campbell:2008:DRT:1636642.1636651, Omar:2012:ACC:2337223.2337324}, leading to lower productivity \cite{Omar:2012:ACC:2337223.2337324}.

\subsection{Language-External Approaches}
\begin{figure}
\begin{center}
\includegraphics[scale=.45]{approaches.pdf}
\end{center}
\vspace{-20px}
\caption{\small (a) With the language-external approach, novel features are packaged into separate languages and tools. Clients of an API can only safely and naturally use it if the interface uses common constructs (the \emph{compatibility problem}). (b) With the active library approach, there is one extensible host language and the compile-time and edit-time logic governing novel constructs is expressed within libraries. If the extension mechanism guarantees the safety of arbitrary compositions of extensions, the necessary primitives can simply be imported by library clients as needed, and so interoperability is not a problem.}
\label{approaches}
\end{figure}
